### 2014-09-23 RFCs/HDF5/VOL/user_guide/plugin.tex
add example
Former-commit-id: 06d8b556668e3dd53df67be09620df7dc29f6629

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
r object GET callback */
typedef enum H5VL_object_get_t {
    H5VL_REF_GET_NAME,                 /* object name                       */
    H5VL_REF_GET_REGION,               /* dataspace of region               */
    H5VL_REF_GET_TYPE                  /* type of object                    */
} H5VL_object_get_t;
\end{lstlisting}

@@

\item {\tt H5VL\_REF\_GET\_REGION}, to retrieve a region reference
  contained in {\tt obj}:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the dataspace created
    from the region reference.
  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference
    (should be {\tt H5R\_DATASET\_REGION}.
  \item {\tt void *ref} (IN): the region reference to open.
  \end{enumerate}

>>>>

The {\tt get\_type} argument is an {\tt enum}:
\begin{lstlisting}
/* type for object GET callback */
typedef enum H5VL_object_get_t {
    H5VL_REF_GET_NAME,                 /* object name                       */
    H5VL_REF_GET_REGION,               /* dataspace of region               */
    H5VL_REF_GET_TYPE                  /* type of object                    */
} H5VL_object_get_t;
\end{lstlisting}

@@

\item {\tt H5VL\_REF\_GET\_REGION}, to retrieve a region reference
  contained in {\tt obj}:
  \begin{enumerate}
  \item {\tt hid\_t *ret\_id} (OUT): buffer for the dataspace created
    from the region reference.
  \item {\tt H5R\_type\_t ret\_type} (IN): type of region reference
    (should be {\tt H5R\_DATASET\_REGION}).
  \item {\tt void *ref} (IN): the region reference to open.
  \end{enumerate}
